Rutgers Autonomous Aircraft Team\\Technical Report\\2010 AUVSI UAS Competition

### 2010-05-25 paper/paper.tex
table headings

\begin{figure} [H]
	\centering
		\begin{tabular}{ccc}
		\\{\bf altitude (ft)} & {\bf pixel width at 0$^{\circ}$ (in)} & {\bf pixel width at 45$^{\circ}$ (in)} \\
	       100 &       0.38 &       0.54 \\
	       200 &       0.76 &       1.08 \\
	       300 &       1.14 &       1.62 \\
	       400 &       1.52 &       2.16 \\
	       500 &       1.90 &       2.69 \\
		\end{tabular}
		\caption[Pixel Width Mapping]{Linear resolution per pixel as a function of altitude, at directly below flight path and \degrees{45} off flight path}
		\label{fig:pixelmapping}
\end{figure}

>>>>

\begin{figure} [H]
	\centering
		\begin{tabular}{ccc}
		\\{\bf Altitude (ft)} & {\bf Pixel width at 0$^{\circ}$ (in)} & {\bf Pixel width at 45$^{\circ}$ (in)} \\
	       100 &       0.38 &       0.54 \\
	       200 &       0.76 &       1.08 \\
	       300 &       1.14 &       1.62 \\
	       400 &       1.52 &       2.16 \\
	       500 &       1.90 &       2.69 \\
		\end{tabular}
		\caption[Pixel Width Mapping]{Linear resolution per pixel as a function of altitude, at directly below flight path and \degrees{45} off flight path}
		\label{fig:pixelmapping}
\end{figure}
